%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
% !TeX spellcheck = en
\documentclass{resume} % Use the custom resume.cls style
\usepackage[colorlinks=true, linkcolor=cyan, urlcolor=cyan]{hyperref}
\urlstyle{same}

\usepackage[left=0.7in,top=0.5in,right=0.7in,bottom=0.5in]{geometry} % Document margins
\usepackage{graphicx}

\name{Kautilya Tripathi}
\address{\href{https://knrt10.netlify.app/}{knrt10.netlify.app} \\
         \href{mailto:tripathi.kautilya@gmail.com}{tripathi.kautilya@gmail.com}\ \\
         \href{https://www.linkedin.com/in/knrt10/}{in/knrt10} \\
         \href{https://github.com/knrt10/}{github.com/knrt10}}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
  \begin{rSummarySection}
  {
    \item CKS and CKA certified engineer with 7+ years of experience in kernel development, backend web services, distributed systems and cloud infrastructure. Open source maintainer of projects with 3.8K+ stars, specialized in Kubernetes ecosystem technologies with proven impact across security, performance, and developer experience.
  }
  \end{rSummarySection}
\end{rSection}

%----------------------------------------------------------------------------------------
% WORK SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\vspace{0.05cm}

  \begin{rWorkSection}{Microsoft}
                     {India}
                     {Software Engineer 2}
                     {May'21 -- Present} {
    \item \textbf{Reduced security vulnerabilities by 40\%} through implementation of a custom mutating webhook that prevented default ServiceAccount token mounting across 200+ pods, strengthening cluster security posture.
    \item \textbf{Core Maintainer} for \texttt{cloud-api-adaptor} (\href{https://github.com/confidential-containers/cloud-api-adaptor}{GitHub}); led Azure CVM boot support reducing boot time by 35\%, implemented 25+ E2E tests for critical paths, and resolved 15 critical Azure bugs increasing platform stability by 60\%.
    \item Refactored Azure provider code (8,000+ LOC) and authored comprehensive onboarding documentation, decreasing new contributor ramp-up time by 50\% and reducing related GitHub issues by 70\%.
    \item \textbf{Core Maintainer} for \texttt{Headlamp} (\href{https://github.com/kubernetes-sigs/headlamp}{GitHub - 3.8K+ stars}); orchestrated 3 major feature releases including WebSocket multiplexer (40\% performance boost), dynamic clusters (serving 500+ users), and UI-driven cluster management.
    \item Engineered thread-safe WebSocket wrapper that eliminated 100\% of concurrency issues, enabling stable multi-cluster support for 30+ simultaneous connections under high load conditions.
    \item Drove test quality initiatives: increased backend test coverage from 65\% to 80\%, expanded E2E tests from 1 to 16, restored CI pipeline with 40\% faster build times, and introduced POM structure reducing test maintenance by 35\%.
    \item Resolved 25+ high-impact bugs including kubeconfig fallback validation, EKS authentication (impacting 150+ users), recursive port-forward loading, and token refresh synchronization for WebSockets.
    \item Enhanced Helm developer experience: implemented schema validation reducing deployment errors by 75\%, added PVC validation for storage requests, integrated ingress label support, and configured OIDC multi-method authentication used across 300+ deployments.
    \item Authored Falco plugin; collaborated directly with Falco maintainers, strengthening CNCF project integrations and expanding ecosystem reach by 25\%.
    \item Mentored Linux Foundation mentee over 3 months with 100\% successful project completion rate; guided implementation of plugin installer container and facilitated weekly technical syncs.
    \item Represented Headlamp at KubeCon North America (1,200+ attendees) and FOSSASIA Hanoi; published 3 technical blogs (5,000+ views) and submitted 2 KubeCon CFPs, increasing community engagement by 40\%.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{Kinvolk}
                     {Remote, India}
                     {Cloud Infrastructure Engineer}
                     {June'20 -- May'21} {
    \item \textbf{Led end-to-end release management} for Lokomotive (\href{https://github.com/kinvolk/lokomotive/}{GitHub}) v0.5.0 and v0.9.0, coordinating 120+ PRs and authored release documentation; contributed 140+ commits impacting over 620 files (35,000+ insertions, 12,000+ deletions).
    \item \textbf{Architected security enhancements}, including implementing a mutating admission webhook for Kubernetes and in-cluster pod traffic encryption using WireGuard, reducing vulnerability exposure by 65\%.
    \item \textbf{Migrated 5 core components to Helm} (MetalLB, Dex, Gangway, httpbin, Prometheus), standardizing deployment methodology and reducing maintenance overhead by 70\%; enabled auto-reloading configs via annotation hash.
    \item \textbf{Enhanced CI/CD pipeline} by implementing GitHub Actions workflows that reduced pipeline execution time by 35\% compared to previous Concourse setup.
    \item Improved infrastructure performance by implementing CPU manager policy, network MTU optimization, and cluster auto-scaling, resulting in 40\% better throughput for compute-intensive workloads.
    \item Developed comprehensive testing framework with 50+ new tests, increasing test coverage by 85\% and reducing post-deployment issues by 70\%.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{Hackerrank}
                     {Bengaluru, India}
                     {SDE Intern}
                     {Jan'20 -- May'20} {
    \item Developed complete backend in Ruby for new "Code Review" question type, reducing senior engineer hiring time by 30\% and improving candidate evaluation accuracy by 45\%.
    \item Deployed and configured high-availability Kubernetes cluster for production code review service, achieving 99.9\% uptime.
    \item Created streamlined workflow that processed 200+ code reviews daily with an average response time under 2 seconds. \href{https://drive.google.com/file/d/1o1cM7VUnvcKaShnM1XLyEChmaIrFrKEh/view}{Preview of workflow}
  }
  \end{rWorkSection}

  \begin{rWorkSection}{The Linux Foundation}
                           {Remote}
                           {Open Mainframe Intern}
                           {June -- Sep '19}
  {
    \item Built 15+ optimized Docker images for s390x architecture on SUSE, reducing image size by 35\% and implementing an automated synchronization bot resulting in 100\% consistency between DockerHub and GitHub.
    \item Established CI/CD pipeline using Jenkins that reduced build times by 40\% and eliminated manual deployments. \href{https://github.com/openmainframeproject-internship/DockerHub-Development-Stacks/}{Project Repository} and \href{https://github.com/knrt10/docker-hub-development-stacks-bot/}{Bot Repository}.
  }                         
  \end{rWorkSection}

  \begin{rWorkSection}{Rocket.Chat}
                      {Remote}
                      {Google Summer of Code Student}
                      {May -- Sep '19}
  {
    \item Engineered real-time monitoring system for Livechat product that increased customer response rate by 40\% and improved agent productivity by 25\%. Successfully completed project with 95\% test coverage. \href{http://bit.ly/2kGqWt2}{GSoC Work Report}.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{Atlan}
                     {New Delhi, IN}
                     {Software Development Intern (Backend)}
                     {Jan -- July '19}
  {
    \item Engineered Baseline Upload system for the company's data collection software platform.
    \item Architected and rebuilt Collect's File Upload system, achieving 99\% improvement in speed and error handling reliability. Applied Jmeter and Blazemeter for comprehensive load testing and deployed to development and staging environments.
    \item Developed scalable task queues and workers using SQS and RabbitMQ, optimizing data processing throughput.
    \item Engineered module response validation system in Golang, enhancing data integrity and validation accuracy.
  }
  \end{rWorkSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
\vspace{0.05cm}
  \begin{rProjectSection}
    \item \textbf{kubernetes-basicLearning} -- Kubernetes educational repository with 2.9K+ stars, providing step-by-step guides. \href{https://github.com/knrt10/kubernetes-basicLearning/}{GitHub Repository}
    \item \textbf{gRPC-cache} -- High-performance in-memory Key/Value store using gRPC with 5ms average response time. \href{https://github.com/knrt10/gRPC-cache}{GitHub Repository}
    \item \textbf{Typeracer-cli} -- Interactive terminal-based touch typing trainer with 300+ downloads. \href{https://github.com/p-society/typeracer-cli/}{GitHub Repository}
    \item \textbf{asciiConvert} -- Terminal ASCII art generator with customization options. \href{https://github.com/knrt10/asciiConvert/}{GitHub Repository}
    \item Additional projects available at \href{https://knrt10.github.io/projects/}{knrt10.github.io/projects}
  \end{rProjectSection}

  \begin{rBlurbSection}
    \item {\em Open-source contributions:}
      I am an active OSS contributor. My \href{http://bit.ly/2kdr9Ui}{\textbf{Merged PR's}} and \href{http://bit.ly/2kxjvV9}{\textbf{open PR's}}.
  \end{rBlurbSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Certificate Section
%----------------------------------------------------------------------------------------

\begin{rSection}{Certificates}
\vspace{0.05cm}
  \begin{rProjectSection}
    \item \textbf{Certified Kubernetes Security Specialist (CKS)} -- Linux Foundation/CNCF Certification \href{https://www.credly.com/badges/05e37407-4ea5-4a88-b8c8-4e26235d7da1}{December 2021 - December 2023}
  \end{rProjectSection}
  \begin{rProjectSection}
    \item \textbf{Certified Kubernetes Administrator (CKA)} -- Linux Foundation/CNCF Certification \href{https://www.credly.com/badges/e93b0ba2-51ea-41b3-82ba-10cf4d67ac70}{December 2020 - December 2023}
  \end{rProjectSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Mentorship Section
%----------------------------------------------------------------------------------------

\begin{rSection}{Mentorship}
\vspace{0.05cm}
  \begin{rProjectSection}
    \item \textbf{Linux Foundation LFX Mentorship Program} -- Primary Mentor for \href{https://mentorship.lfx.linuxfoundation.org/project/992fc67e-ff9e-41fd-8062-28ec8733903f}{Headlamp project}, guiding mentee through feature development, code review, and open source best practices. Successfully led mentee to complete project deliverables with 100\% completion rate.
  \end{rProjectSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Talks Section
%----------------------------------------------------------------------------------------

\begin{rSection}{Talks}
\vspace{0.05cm}
  \begin{rProjectSection}
    \item \textbf{FOSSASIA Conference, Vietnam} -- Presented "Illuminating Open Source: Navigating Kubernetes with Headlamp" \href{https://eventyay.com/e/55d2a466/cfs/session/9010}{(Session Link)}
    \item \textbf{The Linux Foundation, Open Source Summit, Lyon} -- Gave a talk regarding the work on Open Mainframe project. Refer \href{https://user-images.githubusercontent.com/24803604/68012174-99a5a680-fc89-11e9-8c8e-800e68b8c231.jpeg}{Image} and \href{https://drive.google.com/file/d/1z2dhNwudUs8BYJRzIXL70UH7htLJasf0/view}{Slides}
  \end{rProjectSection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\vspace{0.05cm}
  \begin{rEducationSection}{International Institute of Information Technology, Bhubaneswar}
                           {Aug '16 -- June '20}
                           {Bachelor of Technology in Computer Science and Engineering (6.85/10)}
  \end{rEducationSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\vspace{0.05cm}
  \begin{rBlurbSection}
    \item \textbf{Languages:} Go, TypeScript/JavaScript, Python, Ruby, Bash, C/C++
    \item \textbf{Cloud \& Infrastructure:} Kubernetes, Docker, Helm, Azure, AWS, GCP, GitHub Actions, CI/CD, Jenkins
    \item \textbf{Web Technologies:} gRPC, WebSockets, REST, GraphQL, React, Node.js
    \item \textbf{Tools \& Frameworks:} Prometheus, Falco, WireGuard, MetalLB, Dex, OIDC
  \end{rBlurbSection}
\end{rSection}

\end{document}
